Chord: A Versatile Platform for Program Analysis

### 2011-03-30 main/doc/example.tex
documentation edits

\chapter{An Example Run of Chord}
\label{chap:example}

@@

\begin{verbatim}
    example/
        src/
            foo/
                Main.java
                ...
        classes/
            foo/
                Main.class
                ...
        lib/
            src/
                taz/
                    ...
            jar/
                taz.jar
        chord.properties
\end{verbatim}

@@

To run Chord on the above program, run the following command in
Chord's {\tt main/} directory:

\begin{verbatim}
    prompt> ant -Dchord.work.dir=<...>/example run
\end{verbatim}

@@

\begin{verbatim}
    chord.main.class=foo.Main
    chord.class.path=classes:lib/jar/taz.jar
    chord.src.path=src:lib/src
    chord.run.ids=0,1
    chord.args.0="-thread 1 -n 10"
    chord.args.1="-thread 2 -n 50"
\end{verbatim}

@@

\begin{verbatim}
    @Chord(
        name=<JAVA ANALYSIS NAME>
        ...
    )
    public class XYZ extends ... {
        ...
    }
\end{verbatim}

@@

\begin{verbatim}
    # name=<DLOG ANALYSIS NAME>

@@

    # BDD variable order
    .bddvarorder ...
\end{verbatim}
\end{itemize}

To run one or more such analyses, run the following command in Chord's \code{main/} directory:

\begin{verbatim}
    prompt> ant -Dchord.work.dir=<PROGRAM DIR> -Dchord.run.analyses=<ANALYSIS NAME> run
\end{verbatim}

@@

For instance, to run a basic may-alias and call-graph analysis (called 0CFA),
run the following command in Chord's \code{main/} directory:

\begin{verbatim}
    prompt> ant -Dchord.work.dir=<PROGRAM DIR> -Dchord.run.analyses=cipa-0cfa-dlog run
\end{verbatim}

@@

\begin{verbatim}
    Buildfile: build.xml

@@

    BUILD SUCCESSFUL
    Total time: 28 seconds
\end{verbatim}

@@

    BUILD SUCCESSFUL
    Total time: 26 seconds
\end{verbatim}

>>>>

\xname{example}
\chapter{An Example Run}
\label{chap:example}

@@

\begin{framed}
\begin{verbatim}
example/
    src/
        foo/
            Main.java
            ...
    classes/
        foo/
            Main.class
            ...
    lib/
        src/
            taz/
                ...
        jar/
            taz.jar
    chord.properties
\end{verbatim}
\end{framed}

@@

To run Chord on the above program, run the following command in
Chord's main directory:

\begin{framed}
\begin{verbatim}
ant -Dchord.work.dir=<...>/example run
\end{verbatim}
\end{framed}

@@

\begin{framed}
\begin{verbatim}
chord.main.class=foo.Main
chord.class.path=classes:lib/jar/taz.jar
chord.src.path=src:lib/src
chord.run.ids=0,1
chord.args.0="-thread 1 -n 10"
chord.args.1="-thread 2 -n 50"
\end{verbatim}
\end{framed}

@@

\begin{framed}
\begin{verbatim}
@Chord(
    name=<JAVA ANALYSIS NAME>
    ...
)
public class XYZ extends ... {
    ...
}
\end{verbatim}
\end{framed}

@@

\begin{framed}
\begin{verbatim}
# name=<DLOG ANALYSIS NAME>

@@

# BDD variable order
.bddvarorder ...
\end{verbatim}
\end{framed}
\end{itemize}

To run one or more such analyses, run the following command in Chord's main directory:

\begin{framed}
\begin{verbatim}
ant -Dchord.work.dir=<PROGRAM DIR> -Dchord.run.analyses=<ANALYSIS NAME> run
\end{verbatim}
\end{framed}

@@

For instance, to run a basic may-alias and call-graph analysis (called 0CFA),
run the following command in Chord's main directory:

\begin{framed}
\begin{verbatim}
ant -Dchord.work.dir=<PROGRAM DIR> -Dchord.run.analyses=cipa-0cfa-dlog run
\end{verbatim}
\end{framed}

@@

\begin{framed}
{\small
\begin{verbatim}
Buildfile: build.xml

@@

BUILD SUCCESSFUL
Total time: 28 seconds
\end{verbatim}
}
\end{framed}

@@

BUILD SUCCESSFUL
Total time: 26 seconds
\end{verbatim}
}
\end{framed}

### 2011-03-30 main/doc/user_guide.tex
documentation edits

\htmlonly{
	\newcommand\code[1]{{\tt #1}}
	\newcommand\url[1]{\xlink{#1}{#1}}
	\newenvironment{framed}{\xmlattributes*{table}{border=1 frame=box rules=none cellpadding=8}\begin{tabular}{l}}{\end{tabular}}
}

@@

\newenvironment{mytable}[1]
	{\htmlattributes*{table}{border=1 cellpadding=10}\begin{tabular}{#1}}
	{\end{tabular}}

>>>>

\htmlonly{
	\newcommand\code[1]{{\tt #1}}
	\newcommand\url[1]{\xlink{#1}{#1}}
	\newenvironment{framed}
		{\xmlattributes*{table}{border=1 frame=box rules=none cellpadding=8 bgcolor=CCFFFF width=100%
		}\begin{tabular}{l}}{\end{tabular}}
}

@@

\newenvironment{mytable}[1]{\htmlattributes*{table}{border=1 cellpadding=10}\begin{tabular}{#1}}{\end{tabular}}
